The abundance of Bullet Groups in $\Lambda$CDM

### 2014-03-08 paper/ms.tex
Update ms.tex

In this Letter we present prediction for the abundance of group-like
systems that might show a DM-baryon displacement. To this end we use a
N-body cosmological simulation with such a resolution that allows us
to identify multimodal dark matter clumps in the circular velocity
range $300-1000$\kms.

This paper is organized as the follows. In Section
\ref{sec:simulation} we present the simulation and the halo catalogs
used in this work. We continue in Section \ref{sec:setup} with the
geometry of the problem at hand and the measurements setup. Next in
Section \ref{sec:results} we present our results to finish with a
discussion and conclusion in Sections \ref{sec:discussion} and
\ref{sec:conclusions}.

@@

For each host halo in the sample we find its most massive
sub-halo. Each pair host/sub-halo is considererd as a potential Bullet
Group and is kept for the measurement and analysis described in the
next section.

@@

As a first approximation there are two quantities that are available
from observations of these Bullet-like systems. The projected distance
between two dominand dark matter clumps and the ratio of the
galaxies' luminosities associated to them. From the simulation point
of view this can be translated into the 2D projected values of
$||\vec{r}||$, its value relative to the virial radius $D_{\rm off}=
||\vec{r}||_{\rm 2D}/R_{\rm vir}$ and the ratio of the circular velocities
of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. In a higher degree
of detail, in order to gaint better insight we use
the sub-structure velocity as a fraction of the host's circular
velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
of the interaction.  Finally, we also measure the geometry of each
interaction through the values for $\mu$.

All the physical quantities described above can be used to describe
the tree main stages in a bullet-like encounter. First, the sub-halo
crosses the virial radius of the host halo starting a head on
collission, $||\vec{r}||/R_{\rm vir}\approx 1$ and
$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
the center of the host halo $||\vec{r}||/R_{\rm vir} < 1.0$ and
$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
this quantities in Section XXX to fully characterize the different
kind of interactions observed in the Bolshoi simulation.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{New_figures/figure_2.eps}
\end{center}
\caption{
  Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

>>>>

In this Letter we present prediction for the abundance of group-like
systems that might show a DM-baryon displacement. To this end we use a
N-body cosmological simulation with such a resolution that allows us
to identify multimodal dark matter clumps in the circular velocity
range $300-700$\kms.

This paper is organized as the follows. In Section
\ref{sec:simulation} we present the simulation and the halo catalogs
used in this work. We continue in Section \ref{sec:setup} with the
geometry of the problem at hand and the measurements setup. Next in
Section \ref{sec:results} we present our results to finish with a
discussion and conclussion in Sections \ref{sec:discussion} and
\ref{sec:conclussions}.

@@

For each host halo in the sample we find its most massive
sub-halo. Each pair host/sub-halo is considered as a potential Bullet
Group and is kept for the measurement and analysis described in the
next section.

@@

As a first approximation there are two quantities that are available
from observations of these Bullet-like systems. The projected distance
between two dominant dark matter clumps and the ratio of the
galaxies luminosities associated to them. From the simulation point
of view this can be translated into the 2D projected values of
$||\vec{r}||$, its value relative to the virial radius $D_{\rm off}=
||\vec{r}||_{\rm 2D}/R_{\rm vir}$ and the ratio of the circular velocities
of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. In a higher degree
of detail, in order to gaint better insight we use
the sub-structure velocity as a fraction of the host's circular
velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
of the interaction.  Finally, we also measure the geometry of each
interaction through the values for $\mu$.

All the physical quantities described above can be used to describe
the three main stages in a bullet-like encounter. First, the sub-halo
crosses the virial radius of the host halo starting a head on
collission, $||\vec{r}||/R_{\rm vir}\approx 1$ and
$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
the center of the host halo $||\vec{r}||/R_{\rm vir} < 1.0$ and
$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
this quantities in Section XXX to fully characterize the different
kind of interactions observed in the Bolshoi simulation.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{New_figures/figure_2.eps}
\end{center}
\caption{
  Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continuous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}
